Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-24 background_and_systematic.tex
Rephrased and rewrote a couple of sections for greater emphasis and to bring in line with more of the DCs suggestions.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, DVCS/BH events were generated using a Monte Carlo simulation of
the spectrometer that included them. \blue{An event
generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation} because it describes the data well and to keep consistency with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data.  In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated DVCS/BH data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. These contributions are summarised in Table
\ref{table_systematic_contributions_0607}.

@@

\blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state. As the recoiling proton is not detected the separation of the latter events is not possible.}
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``\blue{A}ssoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform the estimation is described in detail in
Ref.~\cite{Air08}.

>>>>

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. \blue{An event
generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation} because it describes the data well and to keep consistency with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data. In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. These contributions are summarised in Table
\ref{table_systematic_contributions_0607}.

\blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state. As the recoiling proton is not detected, separation of the latter events from rest of the data sample is not possible due to the experimental technique.}
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``\blue{A}ssoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform the estimation is described in detail in
Ref.~\cite{Air08}.

@@

### 2011-02-24 results.tex
Rephrased and rewrote a couple of sections for greater emphasis and to bring in line with more of the DCs suggestions.

A statistical test was applied in order to check for possible incompatiability between the asymmetry amplitudes extracted from both data sets. Only the statistical uncertainties were employed in this test. The results show that the two data sets are not incompatible. The $A_{\textrm{LU,I}}$, $A_{\textrm{LU,DVCS}}$ and $A_{\textrm{C}}$ asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_release_pic_update_0607_9605_withassoc}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

@@

The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}. The number of analysable events available from the 2006-2007 data set (67815) is approximately three times greater than the number \blue{of} events recorded in the 1996-2005 sample (24817). The  asymmetry amplitudes extracted from the complete 1996-2007 data set are thus weighted towards the 2006-2007 result. \blue{This is not so evident for the beam helicity asymmetry amplitudes} because the beam polarisation was lower in 2006 and 2007.

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish \blue{in this $-t$ region} due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude \blue{is} compatible with zero, as \blue{is} the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.

>>>>

A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from both data sets. Only the statistical uncertainties were employed in this test. The results show that the two data sets are not incompatible. The $A_{\textrm{LU,I}}$, $A_{\textrm{LU,DVCS}}$ and $A_{\textrm{C}}$ asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_release_pic_update_0607_9605_withassoc}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

@@

The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}. The number of analysable events available from the 2006-2007 data set (67815) is approximately three times greater than the number \blue{of} events recorded in the 1996-2005 sample (24817). The  asymmetry amplitudes extracted from the complete 1996-2007 data set are thus weighted towards the 2006-2007 result. \blue{This weighting towards the 2006-2007 result is not so evident for the beam helicity asymmetry amplitudes} because the beam polarisation was lower in 2006 and 2007.

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish \blue{in this $-t$ region} due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude \blue{is} compatible with zero, as \blue{is} the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands \blue{associated with} the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.

### 2011-02-24 summary.tex
Fixed some typos and rewrote some parts for clarification
Rephrased and rewrote a couple of sections for greater emphasis and to bring in line with more of the DCs suggestions.

Beam helicity and beam charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.

A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The \blue{resulting} \blue{beam charge} asymmetry amplitudes represent the statistically \blue{most} precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this simultaneous extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic of the beam charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are \blue{compared to} calculations from ongoing work to fit GPD models to experimental data. \blue{This model fit ~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 Ref.~\cite{Air09}. \blue{The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.}

>>>>

Beam helicity and beam charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The \blue{resulting} \blue{beam charge} asymmetry amplitudes represent the statistically \blue{most} precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this simultaneous extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic of the beam charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are \blue{compared to} calculations from ongoing work to fit GPD models to experimental data. \blue{This model fit~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 Ref.~\cite{Air09}. \blue{The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes. All amplitudes are also presented projected in $x_{\textrm{B}}$ in bins of $-t$. No localised features are observed in any particular $t$-bin.}

### 2011-02-24 theory.tex
Rephrased and rewrote a couple of sections for greater emphasis and to bring in line with more of the DCs suggestions.

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97a,Rad97} encompass the familiar parton
distribution functions (PDFs) and nucleon form factors to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the H{\sc ermes}
collaboration has previously published results
\cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
the leptoproduction of real photons from a \blue{nucleus} that can be used to
constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a
hard scattering kernel with a GPD that describes a soft part of the scattering
process.

>>>>

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97a,Rad97} encompass the familiar parton
distribution functions (PDFs) and nucleon form factors to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the H{\sc ermes}
collaboration has previously published results
\cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
the leptoproduction of real photons from a nucleon \blue{or nucleus} that can be used to constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a hard scattering kernel with a GPD that describes a soft part of the scattering process.
